Effect of Physical Treatment in Electrical Conductivity of SU-8-based Carbon Structures

### 2020-03-14 myPapers/SU8_PhysicalTreatment/Effect_of_Physical_Treatment_in_Electrical_Conductivity_of_SU8based_Carbon_Structures/article.tex
su8 paper upload

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%toc: yes
%bookmark: yes
%pagenum: yes
%text-layout: twocolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
\makeatother
\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother
          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
\usepackage{etoolbox}

@@

\title{Polymers for Near-field Electrospinning with Spatial Control
}

\author[]{Antonio Osamu Katagiri Tanaka}
\ead{oskatagiri@gmail.com}
\author[]{H{\'e}ctor Al\'{a}n Aguirre Soto}
\ead{alan.aguirre@tec.mx}

\begin{abstract}
Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement. In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process. Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties. This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics. Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
\end{abstract}
\begin{keyword} 
polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

\end{frontmatter}
\tableofcontents

\section{Fabrication Processes of Polymer Fibers}
~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}. One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}. On the other hand, the understanding of the electrospinning process has improved in the last years.

Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector. The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers. Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.

\bgroup
\fixFloatSize{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}{\includegraphics{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}}{}
\makeatother 
\caption{{Electrohydro-dynamic techniques}}
\label{f-02e0e3cf88d6}
\end{figure}
\egroup

\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process. As Brown et al. \unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used). The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state. The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution. The apparatus used by Brown et al. \unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-1e9a6ae11444}.

\bgroup
\fixFloatSize{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}{\includegraphics{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}}{}
\makeatother 
\caption{{Typical Melt Electrospinning Setup}}
\label{f-1e9a6ae11444}
\end{figure}
\egroup
Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.

The first report of a melt electrospun drug delivery system came from Nagy et al. \unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol. The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning. The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.

This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al. in order to reduce the melting point of the polymer-drug mixture. The temperature drop is desirable to minimize the occurring drug degradation.

Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques. Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.  Lian and Men findings feature the solution-spun fibers to have a porous structure. Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning. In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.

In literature, melt electrospinning has less evidence than the solution approach. However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}. Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.

\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-e0d8f2eb18d4}. \unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers. Sun et al. \unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core. Sun et al. state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning. The shell solution can be modified to make the core solution spunable. It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution. \unskip~\cite{527120:13914968}

\bgroup
\fixFloatSize{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}{\includegraphics{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}}{}
\makeatother 
\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
\label{f-e0d8f2eb18d4}
\end{figure}
\egroup
Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle. On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles. \unskip~\cite{527120:13914748,527120:13914750}. As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector. With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate. The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector. \unskip~\cite{527120:13915304}

\subsection{Stretching forces}

\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector. The typical electrospinning setup applies an electrostatic charge to the polymer fluid at the tip of the needle nozzle, which results in the formation of the Taylor cone \unskip~\cite{527120:13659828}, from which a single polymer jet is ejected to the grounded collector. From the Taylor cone, the supplied polymer jet (typically a polymer solution) accelerates and reduces in diameter. The fiber finally develops with the complete solvent evaporation. Electrospun fibers are prone to splitting with the increase in acceleration, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.

The electrospinning process starts with charging a polymer solution droplet. When a polymer solution is administrated with a syringe pump, solution droplets will fall under the influence of gravity. The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a polymer solution jet\unskip~\cite{527120:12033655}.

Shin et al. \unskip~\cite{527120:13659926} reported that the growth of the whipping instability is one important element within the electrospinning technique. As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and strong electric fields the jet becomes unstable after traveling a short distance.

\paragraph{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction. Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow. Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.

The AC electrospinning setup is similar to that for the DC variant. AC electrospinning apparatus do not require a grounded collector as the current alternates. In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge. The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers. The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $. \unskip~\cite{527120:13443405}

The AC technique has been studied for drug loaded related applications. Balogh et al. \unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques. They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer). Balogh et al. discovered AC and DC electrospinning can produce fibers with all three polymers. However, The AC process allowed the implementation of faster flow rates than in the DC setup. The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $. AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.

\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet. Centrifugal spinning intends to produce fibers by the use of a rotating polymer source. The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation. \unskip~\cite{527120:13535559,527120:13535561}.

\bgroup
\fixFloatSize{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}{\includegraphics{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}}{}
\makeatother 
\caption{{Typical setup used in pressurized gyration Processes}}
\label{f-7cf6ac702e28}
\end{figure}
\egroup
The centrifugal force technique is applied to polymer solutions and melts. This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.  Efforts in centrifugal spinning are focused on drug delivery applications. Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach. Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.

On the other hand, PCL and PVP fibers were generated by Amalorpava et al. \unskip~\cite{527120:13536089}.  Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties. Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.

In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field. The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}. Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector. The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.

\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution. The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate. Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3} .

\bgroup
\fixFloatSize{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}{\includegraphics{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}}{}
\makeatother 
\caption{{Dispensing nozzle used for solution blow spinning or melt blowing. \unskip~\protect\cite{527120:13538056}}}
\label{f-92361290d8c3}
\end{figure}
\egroup
Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning. Oliveira et al. \unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications. On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques. Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods. The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.

Jiang et al.\unskip~\cite{527120:13554126} combined the blowing technique with the electrospinning approach. The blow electrospinning technique implements both electric and gas flow forces to stretch the fibers. Jiang used an apparatus similar to those used in traditional electrospinning. The experimental setup requires a coaxial needle nozzle with a pressurized gas flow along with a potential difference between the dispensing needle and the grounded collector.

\subsubsection{Mechanical force}
\bgroup
\fixFloatSize{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}{\includegraphics{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}}{}
\makeatother 
\caption{{Typical mechanical fiber drawing process}}
\label{f-432d16f420fb}
\end{figure*}
\egroup
Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette. \unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications. \unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}. Touch-spinning comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}). Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers. The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter. The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.

\bgroup
\fixFloatSize{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}{\includegraphics{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}}{}
\makeatother 
\caption{{Touch-spinning technique. First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle. Then the rotating rod 'touches' the polymer precursor. Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.}}
\label{f-f17259e76303}
\end{figure*}
\egroup
The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration. The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}

\subsubsection{Microfluidic forces}The microfluidic spinning technique manipulates and controls the polymer solution in networks of micrometer channels. The channel network are typically embedded in a microfluidic chip, where the solution deposition rate is controlled by active components (pumps and valves) with a computer. Cheng et al. \unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.

On the other hand, Kang et al. \unskip~\cite{527120:13656548} managed to fabricate micro fibers by imitating the "silk spinning" process of spiders. Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control. The current microfluidic spinning approach is not scalable to a large fiber production, however it enables the fabrication of high-complex fibers that are not easily achieved by other methods.

\bgroup
\fixFloatSize{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}{\includegraphics{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}}{}
\makeatother 
\caption{{Microfluidic device used by Kang et al.\unskip~\protect\cite{527120:13656548}}}
\label{f-c0beae2757bf}
\end{figure}
\egroup
Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.

\subsection{Nozzle-to-substrate distance}
\bgroup
\fixFloatSize{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}{\includegraphics{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}}{}
\makeatother 
\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
\label{f-fbe88d27b932}
\end{figure*}
\egroup
Figure~\ref{f-fbe88d27b932}.a, depicts the typical setup for the conventional far-field electrospinning (FFES). As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}. When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process. The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}. The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.

In the intent to achieve controlled fiber deposition, Sun et al. \unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-fbe88d27b932}, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line. Moreover, some mechanical influence is required to deposit fibers precisely. The mechanical force is introduced by moving collector. If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}. Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.

The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale. The short distance allow the production of well aligned fibers within particular designs. [7]

\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition. This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research. Table S1 is a collection of the relevant NFES process parameters and achieved fiber morphology.

Some differences have been discovered between LV-NFES and conventional NFES. Low voltage near field electrospinning produces thinner fibers with lower voltages. Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching. Bisht et al. \unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.

Bisht et al. \unskip~\cite{527120:11973130} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup. Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking. In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $ . The decrease in voltage is prone to produce a controlled polymer jet by reducing the bending instabilities. The authors demonstrate the effectiveness of this technique with the fabrication of suspended fibers, see Figure~\ref{f-52c94fbe4526} .

\bgroup
\fixFloatSize{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}{\includegraphics{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}}{}
\makeatother 
\caption{{Suspended nano fibers of 2 wt \% PEO at 300 V. (a) Six carbon posts connected by nano fibers. (b) Individual nano fiber suspended between the posts. (c) Close up of the suspended nano fiber. \unskip~\protect\cite{527120:11973130}}}
\label{f-52c94fbe4526}
\end{figure*}
\egroup
Chang et al. \unskip~\cite{527120:11974306} developed a scanning tip electrospinning (a continuous NFES) technique to write nano fibers with control patterning. Similar to Bisht et al. \unskip~\cite{527120:11973130}, they also demonstrate that the decrease in the applied electric field yields thinner fibers that can be controlled to develop circular shapes (Figure~\ref{f-9d0c3125e550}) and grids (Figure~\ref{f-32e7d8abb3aa}) on a flat surfaces.

\bgroup
\fixFloatSize{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}{\includegraphics{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}}{}
\makeatother 
\caption{{The three-character Cal is drawn on a silicon chip by a programmable x-y stage. \unskip~\protect\cite{527120:11974306}}}
\label{f-9d0c3125e550}
\end{figure}
\egroup

\bgroup
\fixFloatSize{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}{\includegraphics{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}}{}
\makeatother 
\caption{{A triangular grid pattern. \unskip~\protect\cite{527120:11974306}}}
\label{f-32e7d8abb3aa}
\end{figure}
\egroup
Kim et al. \unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537} . As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path. As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other. The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and 600 $\mu m $ needle to rail (offset) distance, see  . (Applied voltage not explicitly specified for "straight line pattern" and stacking experiments, only stated the implementation of 1.9 $kV $ on "sharp-edged shapes pattern" experiments).

\bgroup
\fixFloatSize{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}{\includegraphics{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}}{}
\makeatother 
\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. \unskip~\protect\cite{527120:11974313}}}
\label{f-927e96fb5537}
\end{figure*}
\egroup

\bgroup
\fixFloatSize{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}{\includegraphics{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}}{}
\makeatother 
\caption{{SEM and CCD camera images of stacked fibers on the conductive pattern when high electric field and low electric field were applied}}
\label{f-24b5148e8358}
\end{figure}
\egroup
Gupta et al.\unskip~\cite{527120:11974310} introduced a new technique to fabricate polymer scaffolds for tissue engineering applications and organ development. The authors implemented two polymer solutions, with POSS-PCU (polyhedral oligomeric silsesquioxane-poly(carbonate-urea)urethane, a non-biodegradable polymer precursor) and with POSS-PCL-PCU (poly- hedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate- urea)urethane, a biodegradable polymer precursor).

As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $. The setup was embedded to a motorized collector capable of controlled programmable motions, see Figure~\ref{f-74de1f00848b}. The proposed technique was able to produce fibers of $150 \mu m $ in diameter with pre-designed patterns.

\bgroup
\fixFloatSize{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}{\includegraphics{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}}{}
\makeatother 
\caption{{Schematic illustration of the electrohydrodynamic process. \unskip~\protect\cite{527120:11974310}}}
\label{f-74de1f00848b}
\end{figure}
\egroup
Wang, et al., Huang, et al., and Chen, et al. \unskip~\cite{527120:11974322,527120:11974323,527120:11974324} experimented with several multi-nozzle near-field electrospinning of aligned nano fibers. The multinozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figures~\ref{f-96ee25855dea} and~\ref{f-4a1a1f58a423}. The authors implemented similar NFES setups where the installed linear array of nozzles is supplied with a constant flow rate of solution.

\bgroup
\fixFloatSize{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}{\includegraphics{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}}{}
\makeatother 
\caption{{Schematic of multi-nozzle near-field electrospinning system \unskip~\protect\cite{527120:11974323}}}
\label{f-96ee25855dea}
\end{figure}
\egroup

>>>>

@@

\title{Effect of Physical Treatment in Electrical Conductivity of SU-8-based Carbon Structures
}

\author[a4afda52a866c]{Saeed Beigiborouleni}
\ead{saeed.beigi@tec.mx}
\author[a4afda52a866c]{Antonio Osamu Katagiri Tanaka}
\ead{oskatagiri@gmail.com}

\address[a4afda52a866c]{
    ITESM MTY\unskip, Av. Eugenio Garza Sada Sur\unskip, Monterrey\unskip, 2501\unskip, N.L.\unskip, Mexico}

\begin{abstract}
[TODO: Re-write when the other sections are completed ...]

The effects of physical treatment in electrical conductivity of SU-8 films are investigated. SU-8 films were fabricated through mechanical treatment and stabilization followed by pyrolyzation and characterized by four-point-probe method. Based on previous evidence, it is expected that the induced stress to increase the electrical conductivity of the carbon films. However, the SU-8 carbon films amendment after pyrolysis is mainly due to degassing losses, rather than strain induced forces, hence the small to none differences between the stress-induced and control samples. [AGREE?]
\end{abstract}
\end{frontmatter}

\section{Introduction}
Nanostructures and nanostructured materials such as nanotubes, thin films, suspended nanofibers, and nanofiber mats exhibit unique properties that make them suitable as circuitry elements, structural materials and analytical sensors within micro-mechanical systems. Carbon-based nanostructures have been of interest due to their low reactivity, good electrical and thermal properties with electrochemical stability\unskip~\cite{708527:16798890}. One technique to fabricate carbon structures is through heat treatment/carbonization of organic materials. Organic materials decompose into simpler compounds when exposed to high temperatures in an inert atmosphere or vaccum\unskip~\cite{708527:16798894}; this process is known as pyrolysis. SU-8 is a well-known negative high transparency UV photoresist (see Figure~\ref{f-d9067a619988}) used as a carbon precursor in recent works\unskip~\cite{708527:16798894,708527:16798991,708527:16798990}.

\bgroup
\fixFloatSize{images/c87f718a-dcb5-4fbe-957b-20a0d5843959-usu8composition.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/c87f718a-dcb5-4fbe-957b-20a0d5843959-usu8composition.png}{\includegraphics{images/c87f718a-dcb5-4fbe-957b-20a0d5843959-usu8composition.png}}{}
\makeatother 
\caption{{SU-8 2000 Series Resists Composition. a) photo initiator; b-c) epoxy groups of different SU-8 monomers; d) solvent}}
\label{f-d9067a619988}
\end{figure}
\egroup
Cardenas-Benitez et al.\unskip~\cite{708527:16798894} studied the pyrolysis-induced shrinkage of photocured SU-8 structures due to the volatilized material/degassing and surface area of the microstructures, where the structures shrank about$70\% $ of their original size. Canton et al.\unskip~\cite{708527:16798990} reported that the shrinkage and elongation of suspended SU-8 fibers during pyrolysis influences the resulting electrical properties. In Canton et al. deposited fibers in supporting walls, as the walls shrink during pyrolysis strain forces elongate the fibers. Evidence states that the electrical conductivity increases when fibers are elongated/stretched with a decrease of their diameter\unskip~\cite{708527:16798990}.

On the other hand, literature suggest that the electrical conductivity of carbon electrodes is enhanced with the execution of mechanical treatments, as the precursor polymer chains align within the fibers. Recent efforts \unskip~\cite{708527:16799034,708527:16799035} report carbon fibers with superior electrical conductivity, where the polymer chains are aligned with the aid of carbon nanotubes and hydro-electromechanical strain via electrospinning processes.

In this paper, the effects of physical treatment in electrical conductivity of SU-8 films. SU-8 films were fabricated through mechanical treatment and stabilization followed by pyrolyzation and characterized by the four-point-probe method. Based on previous evidence, it is expected that the induced stress to increase the electrical conductivity of the carbon films.

\section{Materials and Methods}
[TODO: List used materials and their origin]

[TODO: Detailed preparation of the photoresist films]

\bgroup
\fixFloatSize{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}{\includegraphics{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}}{}
\makeatother 
\caption{{Schematic diagram of the SU-8 carbon film fabrication process. a) . b) . c) . d) . e) . f) . g) . h) . i) . j) . k) . l) . }}
\label{f-471d296f0590}
\end{figure*}
\egroup

\section{Results and discussion}
[TODO: Depict the characterization evidence]

\section{Nomenclature}
[TODO: Add used acronyms and their meaning]
\begin{table}[!htbp]
\def\arraystretch{1}
\ignorespaces 
\centering 
\begin{tabulary}{\linewidth}{LL}
\tbltoprule 
 &
  \\
\tblbottomrule 
\end{tabulary}\par 
\end{table}

\section*{Acknowledgments} [TODO: Don't know if this is required ...]
